---
title: "week_6_code_along"
author: "Danielle Sclafani"
date: "11/14/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)
library(ggpubr)
library(broom)
```

##. Part 2: A rank-based test example (Mann Whitney U)

```{r}
set.seed(1414)
gp_1 <- sample.int(20, size = 15, replace = TRUE)

set.seed(1424)
gp_2 <- sample.int(30, size = 15, replace = TRUE)
```

Is there evidence for a significant difference in ranks (medians) between the populations from which gp_1 and gp_2 were drawn?

```{r}
hist(gp_1)
```

```{r}
hist(gp_2)
```

> why would we choose a rank test?
> 1. not clearly normally distributed from exploratory histograms
> 2. somewhat of a small sample size
> 3. i have decided that ranks, or medians, are a more valuable metric to compare for these data

## Mann-Whitney U test

```{r}
my_mwu <- wilcox.test(gp_1, gp_2)
```

> if the null hypothesis is true, there is a probability of 0.43 that we could have found median values at least as different as ours by chance. We do not reject the Ho in this case.


## Part 3. Simple Linear Regression

```{r}

```



